CMCS 818J Project Milestone Report

### 2012-11-04 doc/algorithm.tex
Adding commented out stuff from the milestone

\documentclass[11pt, letterpaper, oneside]{article}
\usepackage{enumitem}
\usepackage{calc}
\usepackage{ amssymb }

\begin{document}
\section{Algortihm 1: Generate Keys}

	genkey procedure generates a secret and public key.  The public key includes vectors \textbf{L} and \textbf{R} as well as $q$ and $\mathcal{U}$.

%Questions on this step:
%	\begin{enumerate}
%	\item	 In the first algorithm defined on page 10, what does the character in 'sk =  \O' represent? Is that the null set?
%	\end{enumerate}

\section{Algorithm 2: Initialization}
\label{initialize}

@@

%	Questions on this step:
%	\begin{enumerate}
%	\item What are the dimensions of table \textbf{T}?  ( $N \times ?$ )
%	\item What does q mean in the context of $Z_{q}^{k}$?  Is this a set of $k \times 1$ vectors or a set of $q \times k$ matrices?
%	\end{enumerate}

\section{Algorithm 3: updateVerifier}
\subsection{Inputs}
	\begin{enumerate}
	\item $x$ where $x \in \mathcal{U}$ is the current element of the stream
	\item $d_{h}$ current state of $auth(D_{h})$
	\item sk and pk - secret and public key \\
	\end{enumerate}

\subsection{Outputs}
	\begin{enumerate}
	\item $d_{h + 1}$ updated state of $auth(D_{h + 1})$
	\end{enumerate}

@@

\subsection{Questions}
\begin{enumerate}
\item What are the roles of the secret and public key as inputs?  In the previous email, you said the prover generates the secret key and does not output it. Therefore, the verifier can't have any value here for $sk$ besides null.
\end{enumerate}

\section{Algorithm 4: updateProver}
\subsection{Input}
	\begin{itemize}
	\item $x$: $x \in \mathcal{U}$ is the current element of the stream
	\item $pk$:  public key
	\item $D_{h}$: The table, \textbf{T} which represents leaves of the Merkle tree described by the scheme
	\item $auth(D_{h})$: The auxiliary information allowing authentication of the elements in $D_{h}$ including all labels $\lambda(v_{i})$ for internals nodes and $d_{h}$, the root digest of the whole tree.
	\end{itemize}
\subsection{Output}

@@

>>>>

\documentclass[11pt, letterpaper, oneside]{article}
\usepackage{enumerate}
\usepackage{calc}
\usepackage{ amssymb }

\begin{document}

Questions on this step:
\begin{enumerate}
\item	 In the first algorithm defined on page 10, what does the character in 'sk =  \O' represent? Is that the null set?
\end{enumerate}

\subsection{ 2: Initialization}
\label{initialize}

@@

Questions on this step:
\begin{enumerate}
\item What are the dimensions of table \textbf{T}?  ( $N \times ?$ )
\item What does q mean in the context of $Z_{q}^{k}$?  Is this a set of $k \times 1$ vectors or a set of $q \times k$ matrices?
\end{enumerate}

\subsection{ 3: updateVerifier}
\subsubsection{Inputs}
\begin{enumerate}
\item $x$ where $x \in \mathcal{U}$ is the current element of the stream
\item $d_{h}$ current state of $auth(D_{h})$
\item sk and pk - secret and public key \\
\end{enumerate}

\subsubsection{Outputs}
\begin{enumerate}
\item $d_{h + 1}$ updated state of $auth(D_{h + 1})$
\end{enumerate}

@@

%\subsection{Questions}
%\begin{enumerate}
%\item What are the roles of the secret and public key as inputs?  In the previous email, you said the prover generates the secret key and does not output it. Therefore, the verifier can't have any value here for $sk$ besides null.
%\end{enumerate}

\subsection{ 4: updateProver}
\subsubsection{Input}
\begin{itemize}
\item $x$: $x \in \mathcal{U}$ is the current element of the stream
\item $pk$:  public key
\item $D_{h}$: The table, \textbf{T} which represents leaves of the Merkle tree described by the scheme
\item $auth(D_{h})$: The auxiliary information allowing authentication of the elements in $D_{h}$ including all labels $\lambda(v_{i})$ for internals nodes and $d_{h}$, the root digest of the whole tree.
\end{itemize}
\subsubsection{Output}

@@

\section{Matrix Multiplication in Ruby}

\subsection{The \texttt{[row $\times$ column]} multiplication:}
\begin{itemize}
\item $ C = A_{n \times n} \times B_{n \times n}$
\item where $ c_{ij} = \sum\limits_{k=1}^n a_{ik} . b_{kj}   $
\item complexity : $\Theta(n^3)$ \\
\end{itemize}

\subsection{Divide and Conquer}

\begin{itemize}

\item Each of the matrices is divided into four $\frac{n}{2} \times \frac{n}{2}$
\item The multiplication of two $ n \times  n $ matrices is reduced to 8 multiplications of
two $\frac{n}{2} \times \frac{n}{2}$ matrices and four $\frac{n}{2} \times \frac{n}{2}$ matrix additions.
\item recurrence : $T(n) = 8.T. \frac{n}{2} + \Theta(n^2) \rightarrow \Theta(n^3)$ \\
\end{itemize}

\subsection{Strassen's Algorithm}

\begin{itemize}

\item Bulky for implementation and not numerically stable
\item Useful and advantageous for large matrices
\item $ \Theta(n^{log7}) \approx \Theta(n^{2.807})$ \\
\end{itemize}

\subsection{Coppersmith Winograd Algorithm}

\begin{itemize}

\item Theoretical optimum; never used in practice.
\item $ \Theta(n^{2.376}) $ \\
\end{itemize}
